---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)
```

```{css}
body {
  font-family: Georgia, serif;
  color: #2c2c2c;
  padding: 20px;
}

h2 {
  color: #4a90d9;
  border-bottom: 2px solid #4a90d9;
  padding-bottom: 6px;
}

p {
  font-size: 16px;
  line-height: 1.7;
}
```

## Daily Café Drink Observations

This report tracks drinks observed at cafés over a two-week period, focusing on drink type, size, price, and time of day. The data is updated dynamically as new observations are logged.

```{r}
suppressPackageStartupMessages(library(tidyverse))

logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vRpaV2hAWyd5ujhrqoV3zonod4LI6QRkUCaeZARUgJAaRf9IqanNpQS5HTG36xY431Mjpn6MmufFrhC/pub?output=csv")

latest_data <- logged_data %>%
  rename(
    timestamp   = Timestamp,
    drink_type  = drink_type,
    size        = size,
    price       = price_nzd,
    time_of_day = time_of_day
  )

# Summary values
total_obs       <- nrow(latest_data)
mean_price      <- round(mean(latest_data$price), 2)
most_common_drink <- names(sort(table(latest_data$drink_type), decreasing = TRUE))[1]
most_common_time  <- names(sort(table(latest_data$time_of_day), decreasing = TRUE))[1]
```

A total of **`r total_obs`** drinks have been observed so far. The most frequently ordered drink is **`r most_common_drink`**, and most observations were made in the **`r most_common_time`**. The average price of a drink is **$`r mean_price` NZD**.

### Drink Type

The bar chart below shows how many times each type of drink was observed during the logging period.

```{r}
ggplot(latest_data, aes(x = drink_type)) +
  geom_bar(fill = "steelblue") +
  labs(
    title = "Number of Observations by Drink Type",
    x = "Drink Type",
    y = "Count"
  ) +
  theme_minimal()
```

### Time of Day

The bar chart below shows at what time of day drinks were most commonly observed.

```{r}
ggplot(latest_data, aes(x = time_of_day)) +
  geom_bar(fill = "mediumseagreen") +
  labs(
    title = "Number of Observations by Time of Day",
    x = "Time of Day",
    y = "Count"
  ) +
  theme_minimal()
```
